Shapes analysis for time series.

### 2024-05-22 NEURIPS24/paper.tex
up grammarly

Nevertheless, \eqref{eq:general_optimization_problem} asks to define a kernel and a loss in order to perform geodesic shooting \ref{eq:relaxation}, which is the purpose of the following subsection.
\vspace{-1ex}
   \subsection{Application of LDDMM to time series analysis: TS-LDDMM}
   \vspace{-1ex}
%\tcr{Mettre l'applicaiton clair pour les times series}

        \label{section:time_series_specificity}
        This section presents our theoretical contribution: we tailor the LDDMM framework to handle time series data.
        The reason is that applying a general diffeomorphism $\phi$ from $\Rset^{d+1}$ to a time series' graph $\msg(s)$ can result in a set $\phi.\msg(s)$ that does not correspond to the graph of any time series, as illustrated in the \Cref{fig:diffeo}.
        Thus, time series graphs have more structure than a simple 1D curve \cite{glaunes2008large} and deserve their unique analysis, which will prove fruitful as demonstrated in \ref{section:experiments}.

@@

       Similarly, selecting a loss function on sets $\mathscr{L}$ that considers the temporal evolution in a time series' graph is crucial for meaningful comparisons with time series data. Consequently, we introduce the oriented Varifold distance. 
\vspace{-1ex}
       \paragraph{A representation separating space and time.}
       We prove that two time series graphs can always be linked by a time transformation composed of a space transformation. Moreover, a time series graph transformed by this kind of transformation is always a time series graph.
        We define $\Psi_\gamma\in \mcd(\Rset^{d+1}) : (t,x)\in\Rset^{d+1}\to (\gamma(t),x)$ for any $\gamma\in \mcd(\Rset)$ and $\Phi_f:  (t,x)\in\Rset^{d+1}\to (t,f(t,x)) $ for any $f\in \rmC^1(\Rset^{d+1},\Rset^d)$. 
        We have the following representation theorem.
        All proofs are given in \Cref{appendix:proofs}.

>>>>

Nevertheless, \eqref{eq:general_optimization_problem} asks to define a kernel and a loss in order to perform geodesic shooting \eqref{eq:relaxation}, which is the purpose of the following subsection.
\vspace{-1ex}
   \subsection{Application of LDDMM to time series analysis: TS-LDDMM}
   \vspace{-1ex}
%\tcr{Mettre l'applicaiton clair pour les times series}

        \label{section:time_series_specificity}
        This section presents our theoretical contribution: we tailor the LDDMM framework to handle time series data.
        The reason is that applying a general diffeomorphism $\phi$ from $\Rset^{d+1}$ to a time series' graph $\msg(s)$ can result in a set $\phi.\msg(s)$ that does not correspond to the graph of any time series, as illustrated in the \Cref{fig:diffeo}.
        Thus, time series graphs have more structure than a simple 1D curve \cite{glaunes2008large} and deserve their unique analysis, which will prove fruitful as demonstrated in \Cref{section:experiments}.

@@

       Similarly, selecting a loss function on sets $\mathscr{L}$ that considers the temporal evolution in a time series' graph is crucial for meaningful comparisons with time series data. Consequently, we introduce the oriented Varifold distance. 
\vspace{-1ex}
       \paragraph{A representation separating space and time.}
       We prove that two time series graphs can always be linked by a time transformation composed with a space transformation. Moreover, a time series graph transformed by this kind of transformation is always a time series graph.
        We define $\Psi_\gamma\in \mcd(\Rset^{d+1}) : (t,x)\in\Rset^{d+1}\to (\gamma(t),x)$ for any $\gamma\in \mcd(\Rset)$ and $\Phi_f:  (t,x)\in\Rset^{d+1}\to (t,f(t,x)) $ for any $f\in \rmC^1(\Rset^{d+1},\Rset^d)$. 
        We have the following representation theorem.
        All proofs are given in \Cref{appendix:proofs}.
